---
title:  Biol/Math 218 pop quiz 1 + 2
author: Your Name Here
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    downcute_theme: "chaos"
    toc_depth: 3
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "pop_quiz_html"
    )
  })
---

## Introduction

A colleague is interested in testing if
knocking down (disabling) a particular gene impacts
wing length in *Drosophila melanogaster*, common fruit flies.
However, she does not know the natural frequency of *Drosophila* 
wing lengths. To determine this, she measured the wing lengths
of 60 flies (30 male and 30 female).

Her data is provided in `flies.csv`, but she does not
know how to use R.

## Part 01
In the space below, provide a code block that will 

1. Import the data file
2. Produce a properly labeled plot(s) to display the frequencies of the wing lengths in the sample

```{r}
``` 

## Part 02
Below, describe the figure, including the shape of the plot, the distribution 
of wing lengths and the most common wing length(s) in her sample. 

Also, are there any important patterns in the frequency data? If so, provide a biologically
relevant cause of the patterns in the data.

`Answer:`

## Part 03 

A researcher provides you a data set, that includes information about the amount of 
periphyton (a mixture of algae and bacteria) that live in urban streams
in upstate New York. 

The data is provided here:

```{r}
url <- "https://raw.githubusercontent.com/lundquist-ecology-lab/biostatistics/main/example_data/periphyton_data.csv"
periphyton <- read.csv(url, header = TRUE, stringsAsFactors = TRUE)
```
They are interested in producing a plot at the pattern of average chlorophyl a
in the periphyton (a measure of health) and the  pH of the water. However, they are really
busy and know that you are an expert in basic plotting in R and do
not bother to tell you much else about the data.

## Step 1:
Using functions in R, determine what variables were measured in this 
data set. 

Then indicate: 
  - Which variables you are are going to plot
  - Whether they are numeric or categorical
  - State which type of plot you are going to produce and why

## Step 2:
Using the plot() function in R, produce the appropriate plot and
then in two or three sentences, interpret any patterns you see in the data
in a biological way. 

Note: Make sure that your plot is properly labeled and has the appropriate
y and x limits
