---
title:  Biol/Math 218 pop quiz 3
author: Answer sheet
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    downcute_theme: "chaos"
    toc_depth: 3
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "pop_quiz_html"
    )
  })
---

## Introduction 

Your graduate advisor would like you to take a look at some data from a colleague of hers.
This data is found on the website:

"https://raw.githubusercontent.com/lundquist-ecology-lab/NYC_tree_pit_biodiversity/main/data/number_of_tree_pits.csv"

Import the data in the code block below

```{r data_import}

tmp <- tempfile(fileext = ".csv")
download.file(url = "https://raw.githubusercontent.com/lundquist-ecology-lab/NYC_tree_pit_biodiversity/main/data/number_of_tree_pits.csv",
            destfile = tmp)
trees <- read.csv(tmp, header = TRUE, stringsAsFactors = TRUE)
head(trees)

```

She tells you that two students went out to collect insects from tree pits in
New York City and she is not sure if they did an even amount of work and wants you
to summarize the data for her.

This is what she wants to know:

1) How many tree pits in total were collected from?

```{r}

# There is a typo in this data, sometimes that happens and is realatively easy to deal with
trees$number_of_pits <- trees$numer_of_pits
print(sum(trees$number_of_pits))
```
`Answer:`

2) How many tree pits each student collected from?

```{r}

A <- trees$number_of_pits[trees$collector == "A"]
print(sum(A))

B <- trees$number_of_pits[trees$collector == "B"]
print(sum(B))

```
`Answer:`

3) What was the average number of tree pits each student collected from per district?

```{r}
levels(trees$district)

A_data <- subset(trees, trees$collector == "A")

A10 <- sum(A_data$number_of_pits[A_data$district == "D10"])
A7 <- sum(A_data$number_of_pits[A_data$district == "D7"])
A8 <- sum(A_data$number_of_pits[A_data$district == "D8"])
A9 <- sum(A_data$number_of_pits[A_data$district == "D9"])

print(mean(c(A10, A7, A8, A9)))

B_data <- subset(trees, trees$collector == "B")

B10 <- sum(B_data$number_of_pits[B_data$district == "D10"])
B7 <- sum(B_data$number_of_pits[B_data$district == "D7"])
B8 <- sum(B_data$number_of_pits[B_data$district == "D8"])
B9 <- sum(B_data$number_of_pits[B_data$district == "D9"])

print(mean(c(B10, B7, B8, B9)))
```
`Answer:`

4) What are the variances of the number of tree pits each student collected from per district?

```{r}
print(var(c(A10, A7, A8, A9)))
print(var(c(B10, B7, B8, B9)))
```

`Answer:`